Title Goes Here

### 2020-04-28 analysis/paper/paper.Rmd
trimmed

```{r}
#how to put n into the label
mtcars2 <- mtcars %>% 
  group_by(cyl, am) %>% mutate(n = n()) %>% 
  mutate(label = paste0(cyl,'\nN = ',n))

ggplot(mtcars2,
   aes(x = factor(label), y = mpg, color = factor(label))) + 
  geom_point() + 
   xlab('cyl') + 
facet_wrap(~am, scales = 'free_x') +
  theme(legend.position = "none")

## CV with site (n=X)
 cv_by_site_df_label <- 
df_sitename %>% 
  select(-SPstage.Stage) %>% 
  group_by(sitename) %>% 
  add_tally() %>% 
  filter( n > 1) %>% 
   mutate(label = as.factor(paste0(sitename,'\nN = ',n))) %>%   select(-n) %>% 
 nest(-sitename, -label) %>% 
  mutate(cv_by_site = map(data, ~map_df(.x, cv)))

>>>>

```{r}
## CV with site (n=X)
 cv_by_site_df_label <- 
df_sitename %>% 
  select(-SPstage.Stage) %>% 
  group_by(sitename) %>% 
  add_tally() %>% 
  filter( n > 1) %>% 
   mutate(label = as.factor(paste0(sitename,'\nN = ',n))) %>%   select(-n) %>% 
 nest(-sitename, -label) %>% 
  mutate(cv_by_site = map(data, ~map_df(.x, cv)))
